---
title: "Quatro_HW_06"
author: "Mano'ike Delude"
format: 
  html:
    code-fold: true
    code-summary: "Show code"
    theme: minty
---

##Homework Week 06 (Quarto)

*Loading all my libraries*
```{r}
#| warning: false
#| message: false
library(palmerpenguins)
library(tidyverse)
library(kableExtra)
library(plotly)
library(here)
library(lubridate)
library(gganimate)
library(gifski)
```

###This is where data gets imported and cleaned
*Importing the maunalua chemical dataset and using my tydr homework code to process it*
```{r}
#| message: false
##Data
  #read in the .csv for the data and depth
cond_dat <- read_csv(here("Week_05", "data", "CondData.csv"))
depth_dat <- read_csv(here("Week_05", "data", "DepthData.csv"))

##Code

  #adding a new column to the dataframes of the fixed (codable) dates as "datetime"
cd <- cond_dat |>
  #round to the nearest 10sec to match the seconds data in depth_dat
  mutate(datetime = mdy_hms(date), datetime = round_date(datetime, "10 sec")) |>
  select(-date) #drop the old date column
dd <- depth_dat |>
  mutate(datetime = ymd_hms(date)) |>
  select(-date) #drop the old dates here too

  #Joining the two dfs in a single one
cond_depth_dat <- inner_join(cd,dd, by = "datetime") |>
  select(-Serial) |> #This is the same number for everything, and is unnecessary for analysis
  mutate(datetime = round_date(datetime, "minute")) |> #rounding all the dates to the nearest minute
  #collapses the variables into longer table for easier analysis
  pivot_longer(cols = c(Depth, Temperature, Salinity),
               names_to = "Variables",
               values_to = "Values") |>
  drop_na() |> #drops NAs in any row
  group_by(datetime, Variables) |> #sort the data by time recorded and variable
  summarise(means_vals = mean(Values)) #average the values for each variable at every time interval

#cond_depth_dat
 #^left in for checking my work
  

```

###This is where my table code goes

```{r}
table_dat <- inner_join(cd,dd, by = "datetime") |>
  select(-Serial) |> #This is the same number for everything, and is unnecessary for analysis
  mutate(datetime = round_date(datetime, "minute")) |>
    pivot_longer(cols = c(Depth, Temperature, Salinity),
               names_to = "Variables",
               values_to = "Values") |>
  drop_na() |> #drops NAs in any row
  group_by(Variables) |>
  summarize(table_means = means(Values, na.rm=TRUE), 
            table_sd = sd(Values, na.rm=TRUE)) |>
  kbl()
  
```


###This is where my figure code goes
#####**WARNING:** do NOT run this code
It will:
-generate hundreds of frames
-3 times
-make your laptop's RAM really really sad!

Post code I will upload the gif which will make your computer have a much nicer time!
```{r}
#| eval: false
cond_depth_plot <- cond_depth_dat |>
  #plot a line graph of the difference variables over time
  ggplot(aes( x = datetime,
              y = means_vals,
              fill = Variables)) +
  #makes a line series that doesn't stack values of the same date
  geom_line(stat = "identity",
           position = "dodge") +
  #splits the graph into 3 plots in one column (so it's easier to compart the timescale)
  geom_point() +
  facet_wrap(~Variables,
             scales = "free_y",
             ncol = 1) +
  theme(legend.position = "none") +
  #remove legend, unnecessary with facet_wrap labels
  labs(y = "Mean Values") +
  #tidy up
  transition_reveal(datetime)

rendered_facet <- animate(cond_depth_plot, renderer = gifski_renderer())

anim_save(here("Week_06", "output", "Ploting data collection by time and depth.gif"),
          animation = rendered_facet
         )

```
##Results


